Interval Probability for Fuzzy Quantum Theories

### 2016-05-19 prob.tex
prob.tex \section{Quantum Probability Spaces} Updates...

\begin{definition}[Complement; Commutativity;
Independence~\cite{peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called complement. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between event. Given a quantum probability measure $\mu$, two projections
$P_{1}$ and $P_{2}$ are independent if $P_{1}$ and $P_{2}$ commute
and $\mu\left(P_{1}P_{2}\right)=\mu\left(P_{1}\right)\mu\left(P_{2}\right)$.
\end{itemize}
\qed\end{definition}

>>>>

\begin{definition}[Complement; Commutativity~\cite{peres1995quantum,Griffiths2003}]~
\begin{itemize}
\item If $P$ is a projection operator, then $\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P$
is also a projection operator, called complement. It is orthogonal to $P$, has
probability~$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, 
and corresponds to the complement event~$\Omega\backslash E$
in classical probability.
\item Projection operators $P_{1}$ and $P_{2}$ commute if $P_{1}P_{2}=P_{2}P_{1}$.
The product of two projection operators~$P_{1}P_{2}$ is also a projection
operator if and only if they commute. This corresponds to the classical intersection
between events. 
\end{itemize}
\yutsung{The definition of independence is different from different
sources:
\begin{enumerate}
\item In Swart's~\cite{Swart2013}, two $*$-algebras~$\mathscr{A}_{1}$ and
$\mathscr{A}_{2}$ which commute with each other are \emph{logically
independent} if for all probability measure~$\mu_{1}$ on $\mathscr{A}_{1}$ and
$\mu_{2}$ on $\mathscr{A}_{2}$, there is an unique probability measure~$\mu_{1}\otimes\mu_{2}$
on $\mathscr{A}_{1}\otimes\mathscr{A}_{2}$ such that
$\left(\mu_{1}\otimes\mu_{2}\right)\left(A_{1}\otimes
A_{2}\right)=\mu_{1}\left(A_{1}\right)\mu_{2}\left(A_{2}\right)$
for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.\\
Then, Swart proved the Bell inequality on logically independence $*$-algebras
with product state. It is good that independence is tied up with Bell
inequality, but the problem for us is that this defines the independent of
algebras, but not events\ldots\\
\item In Yuan's~\cite{Yuan2012}, given a $\mu$ on an $*$-algebra~$\mathscr{A}$,
two sub-$*$-algebra $\mathscr{A}_{1}$ and $\mathscr{A}_{2}$ are independent
if $\mu\left(A_{1}A_{2}\right)=\mu\left(A_{1}\right)\mu\left(A_{2}\right)$
for all $A_{1}\in\mathscr{A}_{1}$ and $A_{2}\in\mathscr{A}_{2}$.
The same problem as the previous one: this defines the
independent of algebras, but not events\ldots\\
\item In order to understand the definition of independence in~\cite{GuehneKleinmannCabelloEtAl2010},
we need first understand their notation because they focused on the
hidden-variable (HV) models. Let $\lambda$ is the HV, $A_{i}$ is
the measurement of the observable~$A$ at the position $i$ in the
sequence. For example, $A_{1}B_{2}C_{3}$ denotes the sequence of
measuring $A$ first, then $B$, and finally $C$. We assume the outcome
of an observable is deterministic by $\lambda$. For example, the
outcome of $B_{2}$ from the preceding sequence is denoted by $v\left(B_{2}\middle|A_{1}B_{2}C_{3}\right)$.
Then, the outcome of $A$ is independent of whether $B$ is measured
before or after $A$ is $v\left(A_{1}\right)=v\left(A_{2}\middle|B_{1}A_{2}\right)$.\\
If the outcomes of compatible observables are independent for any
HV~$\lambda$, the HV model is non-contextual.\\
Compare to the previous definitions, this definition is appealing
in a sense that projection operators are special cases of observables,
and the definition of independence is tied up with contextuality.
However, before adopting their definition, we need to reformulate
the definition to the usual quantum model....
\end{enumerate}
The definition of independence is interesting, and we definitely need
to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
theorem. However, the definition diverges, and none of them can apply
directly. We may need to check more papers to find the majority or
a more suitable definition...?}
\qed\end{definition}
